Proposed Solution

### 2017-01-24 CAV17/secs/postanal.tex
notes for rahul

@@

Define a directed hypergraph with labeled, weighted edges $H = (V,E)$ such that:

@@

as measured by the learner for that relationship. For notational
convenience, later in this section
we shall define $w_{V_1, V_2, l}$ as the weight of the
hyperedge $(V_1, V_2, l, w)$, and $s_{v_1, v_2, l}$ as the sum of weights
over all hyperedges where $v_1 \in V_1$ and $v_2 \in V_2$.
We will refer to this hypergraph as the {\bf Rule Graph}
in further analysis.

@@

@@

It is also worth noting that how good of a heuristic the $DEGREE$ metric is for
\"importance of a configuration parameter\" is dependent on the coverage
of the learnable predicate set encompassed by $L$. The more this predicate
set covers the true configuration parameter relationships in the system,
the better the heuristic.

@@

>>>>

RULE GRAPH

@@

Define a directed hypergraph with $H = (V,E)$ labeled, weighted edges such that:

@@

as measured by the learner for that relationship. For notational
convenience, later in this section
we shall define $w_{V_1, V_2, l}$ as the weight of the
hyperedge $(V_1, V_2, l, w)$, and $s_{v_1, v_2, l}$ as the sum of weights
over all hyperedges where $v_1 \in V_1$ and $v_2 \in V_2$.
\markk{define s explicity as a sum, using E notation from complexity}
We will refer to this hypergraph as the {\bf Rule Graph}
in further analysis.

@@

Talk more about hyperedges or some shit
\iffalse

@@

It is also worth noting that how good of a heuristic the $DEGREE$ metric is for
importance of a configuration parameter is dependent on the coverage
of the learnable predicate set encompassed by $L$. The more this predicate
set covers the true configuration parameter relationships in the system,
the better the heuristic.

@@

Waste less time explaining the example (that should be maybe 1 or 2 paragraphs) and more time explaining the complexity measure.
\para {Semantics}
